---
title: "AtlasXomics `r project_name` report"
output: 
  rmdformats::robobook 
---
* Standard analysis performed without data integration

> created by AtlasXomics bioinformatics team

# Quality Control
* Filtering criteria is as following:

nFeature_Spatial > `r round(min_nFeature_non_zero, digits = 2)`\
percent.mt < `r round(max_percent_mito, digits = 2)`\
percent_hb < `r round(max_percent_hb, digits = 2)`



```{r on_tiss_stats, fig.width=16, fig.height=9, comment=NA}
on_tiss_stats_r

cat("##### RNA-seq samples #####")
qc_rna
bar_plot_r


cat("##### ATAC-seq samples #####")
frag_tss_Plot
bar_plot_a


```

# Dimensionality reduction and clustering

```{r dimrd, fig.width=16, fig.height=9, comment=NA}

dimrd1_r
dimrd1_a

sample_bar_plots_r
sample_bar_plots_a

cat("##### RNA-seq samples #####")
dimrd3_r

cat("##### ATAC-seq samples #####")
dimrd3_a

cat("##### RNA-seq samples #####")
dimrd4_r

cat("##### ATAC-seq samples #####")
dimrd4_a

```

# Identification of Spatially Variable Features RNA-seq

```{r top_spatial_plots_r, fig.width=16, fig.height=9, comment=NA}

if (rlang::is_empty(top_spatial_plots_r)==TRUE){
    cat("Not Enough features pass min.pct=0.01 and threshold=0.1")

}else{
   top_spatial_plots_r
    }

```

# Identification of Spatially Variable Features ATAC-seq

```{r top_spatial_plots_a, fig.width=16, fig.height=9, comment=NA}

if (rlang::is_empty(top_spatial_plots_a)==TRUE){
    cat("Not Enough features pass Pval < 0.05 and threshold=0.1")

}else{
   top_spatial_plots_a
    }

```
